Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-08-27 doc/paper.tex
changes

          	\item introduce a term ``incorrect vertex''. A vertex is incorrect if it is not covered by any guard.
			\item let $incorrect_{total}$ be the total number of incorrect vertices

@@

			\item in each iteration add such a vertex for which the obj value is minimal

>>>>

          	\item introduce a term ``incorrect point''. For a point from D(P) we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
			\item let $incorrect_{total}$ be the total number of incorrect points from discretisazion $D(P)$

@@

			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
